Online Verification of Commutativity

### 2020-08-13 acmPaper/paper.tex
Added conclusion

\begin{figure}[]
    \centering
    \begin{subfigure}{0.4\textwidth}
        \begin{verbatim}
            var a : meters = 1;
            var b : miles = (miles) a;
            var c : feet = (feet) a;
            define wugs:
                1 miles = 10000 wugs;
                1 foot = 10 wugs;
            var d : wugs = (wugs) a;
        \end{verbatim}
        \caption{A sample program with user defined type conversion.}
    \end{subfigure}

@@

\xxx[as]{Write a conclusion.}

>>>>

\begin{figure}[]
    \centering
    \begin{subfigure}{0.4\textwidth}
        \begin{verbatim}
            var a : meters = 1;
            var b : miles = (miles) a;
            var c : feet = (feet) a;
            define wugs:
                1 mile = 10000 wugs;
                1 foot = 10 wugs;
            var d : wugs = (wugs) a;
        \end{verbatim}
        \caption{A sample program with user defined type conversion.}
    \end{subfigure}

@@

Being able to verify if diagrams commute can be a very useful program analysis tool.
It allows a compiler to make deterministic automatic type conversions and can catch inconsistencies of definition in a program with user defined conversions.
In this paper, we have presented verification algorithms that given a commuting diagram, a new edge, efficiently compute the set of paths that would equal to each other if and only if the diagram would still commute after addition of the edge.

Integrating conversion consistency checks into widely used languages such as scala could provide a lot of value to the program.
Beyond implementation work, this requires an answer to the question of how to write function equality oracles.

In the evaluation section, we found that the graph for the optimal set path checker displayed a peculiar regularity in outliers.
Future work might include investigating this behavior.
